Double White Dwarf Mergers on Adaptive Meshes\\ I. Methodology and Code Verification

### 2015-08-25 papers/wdmerger_I/paper.tex
Adopt the WD composition distribution of Dan et al. (2012), abandoning the old pure CO WD approach. This prompted a number of changes to the probdata module and the way initial model data is stored, including the addition of a new derived type for that data.

At the start of any full simulation, we generate initial model white
dwarfs by integrating the equation of hydrostatic equilibrium, taking
the temperature and composition to be constant, and using the
stellar equation of state.  This results in a single non-linear
equation to find the density in a zone given the conditions in the
zone beneath it:
\begin{equation}
\frac{p_{i+1} - p_i}{\Delta x} = \frac{1}{2} (\rho_i + \rho_{i+1}) g_{i+1/2}.
\end{equation}
This equation is a function of $\rho_{i+1}$ only since the pressure is
uniquely determined by the density in this case. Here, $\rho_i$ and $p_i$
are known, $g_{i+1/2}$ is the gravitational acceleration at the
interface between zones $i$ and $i+1$, found by simply adding up all
the mass from zones $1$ to $i$ to get the enclosed mass,
$M_{i+1/2}$, and then setting $g_{i+1/2} =
-GM_{i+1/2}/r_{i+1/2}^2$. We solve this equation for $\rho_{i+1}$
using a Newton-Raphson iteration.

@@

>>>>

At the start of any full simulation, we generate initial model white
dwarfs by integrating the equation of hydrostatic equilibrium, taking
the temperature to be constant, and using the
stellar equation of state.  This results in a single non-linear
equation to find the density in a zone given the conditions in the
zone beneath it:
\begin{equation}
\frac{p_{i+1} - p_i}{\Delta x} = \frac{1}{2} (\rho_i + \rho_{i+1}) g_{i+1/2}.
\end{equation}
This equation is a function of $\rho_{i+1}$ only since the pressure is
uniquely determined by the density in this case. Here, $\rho_i$ and $p_i$
are known, $g_{i+1/2}$ is the gravitational acceleration at the
interface between zones $i$ and $i+1$, found by simply adding up all
the mass from zones $1$ to $i$ to get the enclosed mass,
$M_{i+1/2}$, and then setting $g_{i+1/2} =
-GM_{i+1/2}/r_{i+1/2}^2$. We solve this equation for $\rho_{i+1}$
using a Newton-Raphson iteration.

@@

The white dwarf composition is determined by the chosen mass. For 
this paper we adopt the scheme of \cite{dan:2012}. Low-mass WDs 
are pure helium; low-to-intermediate-mass WDs are an even carbon-oxygen 
core with a relatively large helium envelope; intermediate-mass 
WDs are a carbon-oxygen core with slightly more oxygen than carbon; 
and, high-mass WDs are composed of oxygen, neon, and magnesium. 
This choice of composition distribution broadly resembles the 
results of stellar evolution calculations in the respective 
mass ranges, though it does not match the calculations in detail.
